---
title: "comparison and combination of manual and app-based digital CT"
author: "Dongni Zhang"
date: "Sep,2022"
output: html_document
---


```{r include=FALSE}
# include packages
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(ggplot2)
#install.packages("pracma")
library(pracma)#AUC
library(rootSolve)
#library(sparsevar)
library(cowplot)
library(metR)
library(scales)
library("RColorBrewer")
library(gridExtra)
```


```{r} 
######################################################
# Epidemic (homogeneous mixing)
# transmission rate: beta
# rate of recovery: gamma
# rate of diagnosis: delta
######################################################

# basic reproduction number (without any intervention)
R0 = beta/gamma
R0

# reproduction number (without any CT but with testing)
R = beta/(gamma+delta)
R 
```

## Digital Tracing only: 

```{r}
######################################################
# Digital tracing: (iterative, full tracing, without delay)
# fraction of using app and following the advice: p_A
######################################################
# two-type branching process:
# type 1: non-app-users
# type 2: app-component
# reproduction number for the branching process: R_D
######################################################
######################################################

R_D = function(beta,gamma,delta, p_A){
  
  # elements of the next generation matrix M: 
  
  m11 = (beta * (1- p_A))/ (gamma + delta)
  m22 = 0 
  trace_M = m11 + m22
  m21 = (beta * p_A)/ (gamma + delta)
  
  x = beta*p_A-gamma-delta + sqrt((beta*p_A+gamma+delta)^2-4*beta*p_A*gamma)
  m12 = ((1-p_A)*x)/(2*p_A*delta)
  
  det_M = (-1)*m12*m21
  
  return(trace_M/2+sqrt((trace_M/2)^2-det_M))
  
  
}

######################################################
# Individual reproduction number: 
# average infections produced by one typical infected
######################################################

R_D_ind = function(beta,p_A,delta,gamma){
  
  R0 = beta/(delta+gamma)
  x = beta*p_A-gamma-delta + sqrt((beta*p_A+gamma+delta)^2-4*beta*p_A*gamma)
  f = ((1-p_A)*x)/(2*p_A*delta)
  N_c = f/(beta*(1-p_A)/(beta*p_A+gamma+delta))
  mu = 1+ (beta*p_A)/(beta*p_A+gamma+delta) * N_c
  result1 = p_A* (f+mu-1)/(mu)
  result2 = (1-p_A)*R0
  
  return(result1+result2)
  
}
```

## Manual Tracing only: 

```{r}
######################################################
# Manual tracing: (iterative, full tracing, without delay)
# probability of being traced: p 
######################################################
# single-type branching process of CT-components
# Component Reproduction number R_m:
# the average number of new components produced by one component
######################################################
######################################################
R_M = function(beta,gamma,delta,p){
  
   x = beta*p-gamma-delta + sqrt((beta*p+gamma+delta)^2-4*beta*p*gamma)
   f = ((1-p)*x)/(2*p*delta)
  
  return(f)
  
}

######################################################
# individual reproduction number: 
# average infections produced by one typical infected
######################################################

R_M_ind = function(beta,p,delta,gamma){
  
  x = beta*p-gamma-delta + sqrt((beta*p+gamma+delta)^2-4*beta*p*gamma)
  f = ((1-p)*x)/(2*p*delta)
  N_c = f/(beta*(1-p)/(beta*p+gamma+delta))
  mu = 1+ (beta*p)/(beta*p+gamma+delta) * N_c
  result1 = (f+mu-1)/(mu)
  return(result1)
  }

```

# Prepare for the heatpmap for R_{D}
```{r}
n_grid = 100
# the probability of using app varying in 
p_app_seq = seq(0.01,0.99,length.out=n_grid)
#p_app_seq
# the testing fraction varying in 
test_fraction = seq(0.01,5/6,length.out=n_grid)

R_app_m=matrix(nrow = n_grid,ncol = n_grid)

for (k in (1:n_grid)) {
  p = p_app_seq[k]
  for (j in (1:n_grid)) {
  delta = test_fraction[j]/(1-test_fraction[j]) *gamma
  R = R_D(beta = 6/7, delta=delta,gamma=1/7,p_A=p)
  R_app_m[j,k] = R
  }
}
```

# Prepare for the heatmap for individual R_D_ind
```{r}

R_ind_app_m=matrix(nrow = n_grid,ncol = n_grid)

for (k in (1:n_grid)) {
  p = p_app_seq[k]
  for (j in (1:n_grid)) {
  delta = test_fraction[j]/(1-test_fraction[j]) *gamma
  R = R_D_ind(beta = 6/7, delta=delta,gamma=1/7,p_A=p)
  R_ind_app_m[j,k] = R
  }
}

```

## Compare the two reproduction numbers R_D and R_D_ind: 
```{r}
pi_vector = seq(0.01,0.99,0.01)
R_D_vec = R_D(beta=6/7,p_A=pi_vector,delta=1/7,gamma=1/7)
R_indD_vec = R_D_ind(beta=6/7,p_A=pi_vector,delta=1/7,gamma=1/7)
data_R_D = data.frame(pi_vector,R_D_vec)
data_R_indD = data.frame(pi_vector,R_indD_vec)

# find when pi=?
R_1 =function(x){
  1-R_D(beta=6/7,p_A=x,delta=1/7,gamma=1/7)
}
# find when pi=? R_ind = 1
R_ind_1 =function(x){
  1-R_D_ind(beta=6/7,p_A=x,delta=1/7,gamma=1/7)
}

pi_c = uniroot.all(R_ind_1, c(0,1))
#or pi_c = uniroot.all(R_1, c(0,1))

ggplot(data_R_D,aes(y=R_D_vec,x= pi_vector))+
  geom_line(aes(color = "R_D"))+
  geom_line(aes(y=R_indD_vec,color = "R_(ind)_D"))+
  labs(color="",x="app-using fraction pi", 
       y="reproduction number",
       title="")+
  geom_vline(xintercept = pi_c, linetype = "dashed")+
  geom_hline(yintercept = 1, linetype = "dashed")+
  theme(text = element_text(size=14))+
  annotate("text", y=0,x=pi_c-0.04,label = "pi_c",
           color="black",size = 4,fontface="bold",angle=0)+
  annotate("pointrange", y=1,x=pi_c,ymin = 0, ymax = 0,
           olour = "black", size = 0.2)


```


## Compare Manual CT and Digital CT 
```{r}
n_grid = 100
# the testing fraction varying in 
test_fraction = seq(0.01,5/6,length.out=n_grid)
################### Digital CT#################################
pi_vec_1 = c()

for (i in 1: (n_grid-1)){ 
  
  R1_a =function(pi){
    1-R_D(beta = 6/7, delta=test_fraction[i]/(1-test_fraction[i]) *gamma,
          gamma=1/7,p_A=pi)
  }
  pi_vec_1 = c(pi_vec_1,uniroot.all(R1_a, c(0,1)))
  
}
# we know that for delta=5/7, already R0=1, we dont need manual CT, i.e. pi=0
pi_vec_1 = c(pi_vec_1,0)

# summarize the data 
data.app = data.frame(test_fraction,pi_vec_1)
colnames(data.app)[2] <- "probability"

pi_sq = c()

for (i in 1: (n_grid-1)){ 
  
  R1_a =function(pi){
    1-R_D(beta = beta, delta=test_fraction[i]/(1-test_fraction[i]) *gamma,
          gamma=gamma,p_A=pi)
  }
  solution = uniroot.all(R1_a, c(0,1))
  pi_sq = c(pi_sq,solution^2)
  
}
# for delta = 5/7, we know R_A=1 when p=0
pi_sq = c(pi_sq,0)

data.app.sq = data.frame(test_fraction,pi_sq)
colnames(data.app.sq)[2] <- "probability"

################### Manual CT#################################

p_vec_1 = c()

for (i in 1: (n_grid-1)){ 
  
  R1_m =function(p_c){
    1-R_M(beta = beta, delta=test_fraction[i]/(1-test_fraction[i]) *gamma,gamma=gamma,p=p_c)
  }
  p_vec_1 = c(p_vec_1,uniroot.all(R1_m, c(0,1)))
  
}
# for delta = 5/7, we know R_M=1 when p=0 
p_vec_1 = c(p_vec_1,0)
# summarize the data 
data.manual = data.frame(test_fraction,p_vec_1)
colnames(data.manual)[2] <- "probability"

# plot the data 
# Effective combination of testing and manual/App tracing: pi and p 
ggplot(data.manual,aes(y = test_fraction, x= probability))+
  geom_line(aes(color="R_M = 1"))+
  geom_line(data=data.app,aes(color="R_D = 1"))+
  labs(color="",x="pi or p", 
       y="delta/(delta+gamma)",
       title="")+
  theme(text = element_text(size=14))+
  theme(legend.position="none")

# plot the data 
# Effective combination of testing and manual/App tracing: pi^2 and p 
ggplot(data.manual,aes(y = test_fraction, x= probability))+
  geom_line(aes(color="R_M = 1"))+
  geom_line(data=data.app.sq,aes(color="R_D = 1"))+
  labs(color="",x="pi^2 or p", 
       y="delta/(delta+gamma)",
       title="")+
  theme(text = element_text(size=14))
```


## Combination of manual and Digital CT 

# First, the process of  N(t)
```{r}
# input: 
# size of the component starts by number of app-users = i,  number of non-app-users = j
# p: probability of successful manual contact tracing
# p_A: probability of using a tracing app and following the advice

# output: 
# data contaning the number of app-users, non-app-users at each event time   
# size of the component starts by number of app-users = i,  number of non-app-users = j
# 
beta = 6/7
gamma= 1/7

delta= 1/7
# so that delta/(delta+gamma) = 1/2

N_c <- function(i,j,p,p_A){
  
  time = c(0)
  n_app_users = c(i)
  n_nonapp_users = c(j)
  
  
  N_1t = i
  N_2t = j
  
  while (N_1t+N_2t > 0) {
    
    # the rates of five events
    r1 = N_1t * beta * p_A + N_2t * beta * p_A * p
    r2 = (N_1t + N_2t) * beta * (1-p_A)  * p
    r3 = (N_1t ) * gamma
    r4 = (N_2t ) * gamma
    r5 = (N_1t+ N_2t) * delta
    
    # new event time 
    rate = r1+r2+r3+r4+r5
    t_event = time[length(time)] + rexp(1, rate)
    time = c(time,t_event)
    
    # decide which event 
    rd = runif(1)
    
    if ( rd < r1/rate) {
# new infection to app-user 
      N_1t = N_1t + 1
      N_2t = N_2t + 0
      n_app_users = c(n_app_users,N_1t)
      n_nonapp_users = c(n_nonapp_users,N_2t)
      
} else if ( rd >= r1/rate & rd < (r1+r2)/rate) {
# new infection to non-app-user 
      N_1t = N_1t + 0
      N_2t = N_2t + 1
      n_app_users = c(n_app_users,N_1t)
      n_nonapp_users = c(n_nonapp_users,N_2t)
} else if ( rd >= (r1+r2)/rate & rd < (r1+r2+r3)/rate) {
# natural recovery of app-user 
      N_1t = N_1t - 1
      N_2t = N_2t + 0
      n_app_users = c(n_app_users,N_1t)
      n_nonapp_users = c(n_nonapp_users,N_2t)
} else if ( rd >= (r1+r2+r3)/rate & rd < (r1+r2+r3+r4)/rate) {
# natural recovery of non-app-user 
      N_1t = N_1t + 0
      N_2t = N_2t - 1
      n_app_users = c(n_app_users,N_1t)
      n_nonapp_users = c(n_nonapp_users,N_2t)
}else {
# diagnosis of either non-app-user or app user
      N_1t =  0
      N_2t = 0
      n_app_users = c(n_app_users,N_1t)
      n_nonapp_users = c(n_nonapp_users,N_2t)
}
    
    
    }
  
  data.component = data.frame(time,n_app_users,n_nonapp_users)
  
  return(data.component)
  
}
```

# Next, function to compute R_DM
```{r}
set.seed(123456)
Reprod_DM <- function(p,p_A){

# component with root as App-user (type-1 individual)
# Area under curve of the number of type-2 individuals (Non-app-users) produced by such component
AUC_N_2_C1 = c()
# Area under curve of number of type-1 individuals (app-users) produced by such component
AUC_N_1_C1 = c()

# run 10000 simulations
for (k in (1:10000)) {
  data_component_a = N_c(i = 1,j = 0,p = p,p_A = p_A)
  cuts = data_component_a$time
  vals_1 = data_component_a$n_app_users
  AUC_1 = 0
  
  for (i in (1:length(cuts))) {
  t_interval = cuts[i+1] - cuts[i]
  area = vals_1[i]*t_interval
  AUC_1 = AUC_1 + area
  
  if (i+1==length(cuts)) break
  }
  
  AUC_N_1_C1 = c(AUC_N_1_C1,AUC_1)
  
  vals_2 = data_component_a$n_nonapp_users
  AUC_2 = 0
  
  for (i in (1:length(cuts))) {
  t_interval = cuts[i+1] - cuts[i]
  area = vals_2[i]*t_interval
  AUC_2 = AUC_2 + area
  
  if (i+1==length(cuts)) break
  }
  
  AUC_N_2_C1 = c(AUC_N_2_C1,AUC_2)
                 
  
}


# component with root as non-App-user (type-2 individual)
# Area under curve of the number of type-2 individuals (Non-app-users) produced by such component
AUC_N_2_C2 = c()
# Area under curve of number of type-1 individuals (app-users) produced by such component
AUC_N_1_C2 = c()

# run 10000 simulations
for (k in (1:10000)) {
  data_component_na = N_c(i = 0,j = 1,p = p,p_A = p_A)
  cuts = data_component_na$time
  vals_1 = data_component_na$n_app_users
  AUC_1 = 0
  
  for (i in (1:length(cuts))) {
  t_interval = cuts[i+1] - cuts[i]
  area = vals_1[i]*t_interval
  AUC_1 = AUC_1 + area
  
  if (i+1==length(cuts)) break
  }
  
  AUC_N_1_C2 = c(AUC_N_1_C2,AUC_1)
  
  vals_2 = data_component_na$n_nonapp_users
  AUC_2 = 0
  
  for (i in (1:length(cuts))) {
  t_interval = cuts[i+1] - cuts[i]
  area = vals_2[i]*t_interval
  AUC_2 = AUC_2 + area
  
  if (i+1==length(cuts)) break
  }
  
  AUC_N_2_C2 = c(AUC_N_2_C2,AUC_2)
                 
  
}

# compute the next-generation matrix
m_11 = mean(AUC_N_2_C1)*p_A*beta*(1-p)
m_21 = mean(AUC_N_2_C2)*p_A*beta*(1-p)
m_12 =(mean(AUC_N_2_C1)+mean(AUC_N_1_C1))*(1-p_A)*beta*(1-p)
m_22 =(mean(AUC_N_2_C2)+mean(AUC_N_1_C2))*(1-p_A)*beta*(1-p)

# compute the largest eigenvalue of next-generation matrix


tr_M = m_11+m_22

det_M = m_11*m_22 - m_12*m_21

  
return(tr_M/2+sqrt((tr_M/2)^2-det_M))

}

```

# Get ready for heatmap of R_DM
```{r}
n_grid = 100

# pi takes values in 
p_app_seq = seq(0,0.99, length.out=n_grid)
#p_app_seq # increment size with 0.99/99=0.01

# p takes values in 
p_manual_seq = seq(0,0.99, length.out=n_grid)

# store the R_DM values in a matrix:
R_DM_m=matrix(nrow = n_grid,ncol = n_grid)
```


```{r}
# start compute R_DM for each combination of p and pi

for (k in (1:n_grid)) {
  
  p_A = p_app_seq[k]
  
  for (j in (1:n_grid)) {
    
  p = p_manual_seq[j] 
  
  set.seed(123456)
  
  R = Reprod_DM(p=p, p_A=p_A)
  
  R_DM_m[j,k] = R
  
  }
}

```

## If we choose small testing fraction 0.2:
```{r}
beta=6/7
gamma=1/7
# choose small delta 
delta_s = 1/28
# the testing fraction
#delta_s/(delta_s+gamma)
delta=delta_s

# Now : R_0 = 4.8
# first, the process of  N(t)

# input: 
# size of the component starts by number of app-users = i,  number of non-app-users = j
# p: probability of successful manual contact tracing
# p_A: probability of using a tracing app and following the advice

# output: 
# data contaning the number of app-users, non-app-users at each event time   
# size of the component starts by number of app-users = i,  number of non-app-users = j

N_c <- function(i,j,p,p_A){
  
  time = c(0)
  n_app_users = c(i)
  n_nonapp_users = c(j)
  
  
  N_1t = i
  N_2t = j
  
  while (N_1t+N_2t > 0) {
    
    # the rates of five events
    r1 = N_1t * beta * p_A + N_2t * beta * p_A * p
    r2 = (N_1t + N_2t) * beta * (1-p_A)  * p
    r3 = (N_1t ) * gamma
    r4 = (N_2t ) * gamma
    r5 = (N_1t+ N_2t) * delta
    
    # new event time 
    rate = r1+r2+r3+r4+r5
    t_event = time[length(time)] + rexp(1, rate)
    time = c(time,t_event)
    
    # decide which event 
    rd = runif(1)
    
    if ( rd < r1/rate) {
# new infection to app-user 
      N_1t = N_1t + 1
      N_2t = N_2t + 0
      n_app_users = c(n_app_users,N_1t)
      n_nonapp_users = c(n_nonapp_users,N_2t)
      
} else if ( rd >= r1/rate & rd < (r1+r2)/rate) {
# new infection to non-app-user 
      N_1t = N_1t + 0
      N_2t = N_2t + 1
      n_app_users = c(n_app_users,N_1t)
      n_nonapp_users = c(n_nonapp_users,N_2t)
} else if ( rd >= (r1+r2)/rate & rd < (r1+r2+r3)/rate) {
# natural recovery of app-user 
      N_1t = N_1t - 1
      N_2t = N_2t + 0
      n_app_users = c(n_app_users,N_1t)
      n_nonapp_users = c(n_nonapp_users,N_2t)
} else if ( rd >= (r1+r2+r3)/rate & rd < (r1+r2+r3+r4)/rate) {
# natural recovery of non-app-user 
      N_1t = N_1t + 0
      N_2t = N_2t - 1
      n_app_users = c(n_app_users,N_1t)
      n_nonapp_users = c(n_nonapp_users,N_2t)
}else {
# diagnosis of either non-app-user or app user
      N_1t =  0
      N_2t = 0
      n_app_users = c(n_app_users,N_1t)
      n_nonapp_users = c(n_nonapp_users,N_2t)
}
    
    
    }
  
  data.component = data.frame(time,n_app_users,n_nonapp_users)
  
  return(data.component)
  
}


# next, function to compute R_DM

set.seed(123456)
Reprod_DM <- function(p,p_A){

# component with root as App-user (type-1 individual)
# Area under curve of the number of type-2 individuals (Non-app-users) produced by such component
AUC_N_2_C1 = c()
# Area under curve of number of type-1 individuals (app-users) produced by such component
AUC_N_1_C1 = c()

# run 10000 simulations
for (k in (1:10000)) {
  data_component_a = N_c(i = 1,j = 0,p = p,p_A = p_A)
  cuts = data_component_a$time
  vals_1 = data_component_a$n_app_users
  AUC_1 = 0
  
  for (i in (1:length(cuts))) {
  t_interval = cuts[i+1] - cuts[i]
  area = vals_1[i]*t_interval
  AUC_1 = AUC_1 + area
  
  if (i+1==length(cuts)) break
  }
  
  AUC_N_1_C1 = c(AUC_N_1_C1,AUC_1)
  
  vals_2 = data_component_a$n_nonapp_users
  AUC_2 = 0
  
  for (i in (1:length(cuts))) {
  t_interval = cuts[i+1] - cuts[i]
  area = vals_2[i]*t_interval
  AUC_2 = AUC_2 + area
  
  if (i+1==length(cuts)) break
  }
  
  AUC_N_2_C1 = c(AUC_N_2_C1,AUC_2)
                 
  
}


# component with root as non-App-user (type-2 individual)
# Area under curve of the number of type-2 individuals (Non-app-users) produced by such component
AUC_N_2_C2 = c()
# Area under curve of number of type-1 individuals (app-users) produced by such component
AUC_N_1_C2 = c()

# run 10000 simulations
for (k in (1:10000)) {
  data_component_na = N_c(i = 0,j = 1,p = p,p_A = p_A)
  cuts = data_component_na$time
  vals_1 = data_component_na$n_app_users
  AUC_1 = 0
  
  for (i in (1:length(cuts))) {
  t_interval = cuts[i+1] - cuts[i]
  area = vals_1[i]*t_interval
  AUC_1 = AUC_1 + area
  
  if (i+1==length(cuts)) break
  }
  
  AUC_N_1_C2 = c(AUC_N_1_C2,AUC_1)
  
  vals_2 = data_component_na$n_nonapp_users
  AUC_2 = 0
  
  for (i in (1:length(cuts))) {
  t_interval = cuts[i+1] - cuts[i]
  area = vals_2[i]*t_interval
  AUC_2 = AUC_2 + area
  
  if (i+1==length(cuts)) break
  }
  
  AUC_N_2_C2 = c(AUC_N_2_C2,AUC_2)
                 
  
}

# compute the next-generation matrix
m_11 = mean(AUC_N_2_C1)*p_A*beta*(1-p)
m_21 = mean(AUC_N_2_C2)*p_A*beta*(1-p)
m_12 =(mean(AUC_N_2_C1)+mean(AUC_N_1_C1))*(1-p_A)*beta*(1-p)
m_22 =(mean(AUC_N_2_C2)+mean(AUC_N_1_C2))*(1-p_A)*beta*(1-p)

# compute the largest eigenvalue of next-generation matrix


tr_M = m_11+m_22

det_M = m_11*m_22 - m_12*m_21

  
return(tr_M/2+sqrt((tr_M/2)^2-det_M))

}

```

# get ready for heatmap of R_DM
```{r}
n_grid = 100

# pi takes values in 
p_app_seq = seq(0,0.99, length.out=n_grid)
#p_app_seq # increment size with 0.99/99=0.01

# p takes values in 
p_manual_seq = seq(0,0.99, length.out=n_grid)

# store the R_DM values in a matrix:
R_DM_ms=matrix(nrow = n_grid,ncol = n_grid)

# start compute R_DM for each combination of p and pi

for (k in (1:n_grid)) {
  
  p_A = p_app_seq[k]
  
  for (j in (1:n_grid)) {
    
  p = p_manual_seq[j] 
  
  set.seed(123456)
  
  R = Reprod_DM(p=p, p_A=p_A)
  
  R_DM_ms[j,k] = R
  
  }
}
```
## Plot the heatmaps for R_D, R_D_ind, R_comb

```{r}

# store all data for heatmaps in a data frame
data_all_D <- expand.grid(testing=test_fraction,app_prob=p_app_seq)
data_all_D$R_D <-c(R_app_m)
data_all_D$R_ind_D <-c(R_ind_app_m)

data_all_DM <- expand.grid(manual_prob=p_manual_seq,app_prob=p_app_seq)
data_all_DM$R_DM = c(R_DM_m)
data_all_DM$R_DM_s = c(R_DM_ms)
```


```{r}
# heatmap for R_D
plot_1 <- ggplot(data_all_D, aes(x=app_prob,y=testing,fill=R_D))+ 
geom_tile()+
labs(title="", y="delta/(delta+gamma)", x="app-using fraction pi")+
scale_fill_distiller(palette = "Spectral",
                     limits = c(0,max(data_all_D$R_D)),
                     "reproduction\nnumber")+
# set contour breaks at desired level 
geom_contour(aes(z = R_D), breaks = 1, col = 'azure',size = 0.5)+
geom_contour(aes(z = R_D), breaks = 10, col = 'black',size = 0.5,linetype ="dashed")+
theme(plot.title = element_text(hjust = 0.5
                                #,face="bold"
                                ))+
theme(text = element_text(size=14))+
geom_text_contour(aes(z = R_D), stroke = 0.1,breaks=1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_D), stroke = 0.1,breaks=10,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))

# heatmap for R_D_ind
plot_2 <-ggplot(data_all_D, aes(x=app_prob,y=testing,fill=R_ind_D))+ 
geom_tile()+
labs(title="", y="delta/(delta+gamma)", x="app-using fraction pi")+
scale_fill_distiller(palette = "Spectral",direction=-1,
                     limits = c(0,max(data_all_D$R_D)),
                     "reproduction\nnumber")+
# set contour breaks at desired level 
geom_contour(aes(z = R_ind_D), breaks = 1, col = 'azure',size = 0.5)+
geom_contour(aes(z = R_ind_D), breaks = 1.5, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_ind_D), breaks = 2, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_ind_D), breaks = 2.5, col = 'black',size = 0.5,linetype ="dashed")+  
theme(plot.title = element_text(hjust = 0.5
                                #,face="bold"
                                ))+
theme(text = element_text(size=14))+
geom_text_contour(aes(z = R_ind_D), stroke = 0.1,breaks=1,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_ind_D), stroke = 0.1,breaks=1.5,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_ind_D), stroke = 0.1,breaks=2,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_ind_D), stroke = 0.1,breaks=2.5,
                  label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+ 
theme(legend.position="none")

# heatmap for R_DM
plot_3 <-ggplot(data_all_DM, aes(y=app_prob,x=manual_prob,fill=R_DM))+ 
geom_tile()+
labs(title="", y="app-using fraction pi", x="manual reporting probability p")+
scale_fill_distiller(palette = "Spectral",
                     limits = c(0,max(data_all_D$R_D)),
                     "R_DM")+
# set contour breaks at desired level
geom_contour(aes(z = R_DM), breaks = 1, col = 'azure',size = 0.5)+
geom_contour(aes(z = R_DM), breaks = 1.5, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_DM), breaks = 2, col = 'black',size = 0.5,linetype ="dashed")+
geom_contour(aes(z = R_DM), breaks = 2.5, col = 'black',size = 0.5,linetype ="dashed")+  
#theme(plot.title = element_text(hjust = 0.5,face="bold"))+
theme(text = element_text(size=14))+
geom_text_contour(aes(z = R_DM), stroke = 0.1,breaks=1,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_DM), stroke = 0.1,breaks=1.5,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_DM), stroke = 0.1,breaks=2,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_DM), stroke = 0.1,breaks=2.5,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+ 
theme(legend.position="none")

# heatmap for R_DM_s when small delta
plot_4 <-ggplot(data_all_DM, aes(y=app_prob,x=manual_prob,fill=R_DM_s))+ 
geom_tile()+
labs(title="", y="app-using fraction pi", x="manual reporting probability p")+
scale_fill_distiller(palette = "Spectral",
                     limits = c(0,max(data_all_D$R_D)),
                     "R_DM")+
# set contour breaks at desired level 
geom_contour(aes(z = R_DM_s), breaks = 1, col = 'azure',size = 0.5)+
geom_contour(aes(z = R_DM_s), breaks = 6, col = 'black',size = 0.5,linetype ="dashed")+
theme(text = element_text(size=14))+
geom_text_contour(aes(z = R_DM_s), stroke = 0.1,breaks=1,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
geom_text_contour(aes(z = R_DM_s), stroke = 0.1,breaks=6,label.placer=label_placer_fraction(frac = 0.5, rot_adjuster = isoband::angle_halfcircle_bottom()))+
theme(legend.position="none")

# 2. Save the legend
#+++++++++++++++++++++++
legend <- get_legend(plot_1)
# 3. Remove the legend 
#+++++++++++++++++++++++
plot_1 <- plot_1 + theme(legend.position="none")
# 4. Arrange ggplot2 graphs with a specific width
#plot_all <-grid.arrange(plot_1, plot_2, plot_3,  plot_4, ncol=2,widths=c(2.3, 2.3))
#grid.arrange(plot_all, legend,ncol=2, widths=c(5, 1))

plot_1
plot_2
plot_3
grid.arrange(plot_4, legend,ncol=2, widths=c(5, 1.4))
```

